---
title: "RWorksheet_Aposaga#4c"
author: "John Philipp Aposaga"
date: "2024-11-04"
output: pdf_document
---
#1
#a
```{r}
mpg <- read.csv("mpg.csv", header = TRUE, sep = ",")
mpg
```   
#b
#The categorical variables are the Manufacturer, Model, Trans, Drv, fl, and class.

#c
#The continuous variables are displ, cty, hwy.

#2
#The manufacturer with the most models in the dataset is Toyota, having 6 different models. The "caravan 2wd" model has the most variations, with 11 different entries.

#a
```{r}
# Group by manufacturer and count unique models
mmc <- mpg %>%
  group_by(manufacturer) %>%
  summarise(unique_models = n_distinct(model)) %>%
  arrange(desc(unique_models))

# Print the result
print(mmc)
```
#b
```{r}
# Base R plotting
barplot(
  mmc$unique_models,
  names.arg = mmc$manufacturer,
  col = "skyblue",
  main = "Number of Unique Models by Manufacturer",
  xlab = "Manufacturer",
  ylab = "Number of Unique Models",
  las = 2,
  cex.names = 0.7
)

# ggplot2 plotting
ggplot(mmc, aes(x = reorder(manufacturer, -unique_models), y = unique_models)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Number of Unique Models by Manufacturer", x = "Manufacturer", y = "Number of Unique Models") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#2a
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
#2b
#Convert the counts into a heatmap for easier visual analysis.In this plot, darker shades indicate higher counts, making it easy to see popular model-manufacturer combinations at a glance. These modifications offer a clearer view of relationships and trends in the dataset.

#3
```{r}
f20 <- mpg[1:20, ]
ggplot()
```






